A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-04-26 manuscript.Rmd
add singularity

>>>>

One usecase in which Docker sometimes can't be used is in high performance computing (HPC).
The simulation we did is computationally expensive enough to warrant the use of a HPC cluster.
To run the simulation on a cluster we require the exact same software, not only on one or two computers, but potentially hundreds.
Docker is a natural solution for this problem and is the defacto standard for cloud computing.
However, Docker requires admin rights, while this is no issue on cloud computing infrastructure it is an issue in classical HPC environments.
Singularity was designed to run without admin rights, while maintaining full compatibility with Docker images.
If you already have a Docker image, you can choose if you want to run this image with Docker or with Singularity.
Anyway, from within the container i.e. for your analysis it does not make any difference.
